reference-hack

### 2022-06-27 jss/appendix.Rmd
knit
clean up repo

Figure \ref{fig:interactive-popup} shows the same information as Figure 9 but using leaflet and popups [@leafpop].

@@

```{r illu-interactive-2, echo = FALSE, fig.align="center", out.height="40%", out.width = "100%", fig.cap = "Linking between multiple plots. The line plots and the map are constructed from shared crosstalk objects (long and nested cubbles). When a point on the time series is selected, the corresponding row in the long cubble will be activated (a). This will link to all the rows with the same id in the long cubble and the row in the nested cubble with the same id (b). Both plots will be updated with the full line selected and the point highlighted on the map (c)."}
knitr::include_graphics(here::here("figures/diagram-keynotes/diagram-keynotes.005.png"))
```

>>>>

Figure \ref{fig:interactive-popup} shows the same information as Figure 9 but using leaflet and popups.

@@

```{r illu-interactive-2, echo = FALSE, fig.align="center", out.height = "35%", out.width = "100%", fig.cap = "Linking between multiple plots. The line plots and the map are constructed from shared crosstalk objects (long and nested cubbles). When a point on the time series is selected, the corresponding row in the long cubble will be activated (a). This will link to all the rows with the same id in the long cubble and the row in the nested cubble with the same id (b). Both plots will be updated with the full line selected and the point highlighted on the map (c)."}
knitr::include_graphics(here::here("figures/diagram-keynotes/diagram-keynotes.005.png"))
```

### 2022-06-27 jss/main.Rmd
clean up repo

```{r setup, echo = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  cache = TRUE,
  fig.path = "figures/"
)

@@

```{r child = here::here("reference-hack.Rmd")}

>>>>

```{r setup, echo = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  cache = TRUE,
  fig.path = here::here("figures/")
)

@@

```{r child = here::here("jss/reference-hack.Rmd")}

### 2022-06-27 jss/main.tex
clean up repo

{\centering \includegraphics[width=1\linewidth]{figures/basic-manip-1}

@@

{\centering \includegraphics[width=1\linewidth]{figures/matching-1}

@@

{\centering \includegraphics[width=1\linewidth]{figures/netcdf-1}

>>>>

{\centering \includegraphics[width=1\linewidth]{/Users/hzha400/Documents/research/paper-cubble/figures/basic-manip-1}

@@

{\centering \includegraphics[width=1\linewidth]{/Users/hzha400/Documents/research/paper-cubble/figures/matching-1}

@@

{\centering \includegraphics[width=1\linewidth]{/Users/hzha400/Documents/research/paper-cubble/figures/netcdf-1}

### 2022-06-27 jss/reference-hack.Rmd
clean up repo

```{r}
tex <- readLines(here::here("references.bib"))

b <- tex %>% stringr::str_extract("\\@(article|techreport|misc|Manual|Book)\\{.+,")
b <- b[!is.na(b)]
ref_head <- b %>% stringr::str_replace("\\@(article|techreport|misc|Manual|Book)\\{", "") %>% 
  stringr::str_replace(",", "")

res <- paste0("@", ref_head, collapse = ", ")
```

>>>>

```{r}

tex <- readLines(here::here("references.bib"))
b <- tex %>% stringr::str_extract("\\@(article|techreport|misc|Manual|Book)\\{.+,")
b <- b[!is.na(b)]
ref_head <- b %>% stringr::str_replace("\\@(article|techreport|misc|Manual|Book)\\{", "") %>% 
  stringr::str_replace(",", "") 
res <- paste0("@", ref_head, collapse = ", ")
```
